### 2022-07-03 Papers/ICCC-2023/sections/introduction.tex
.

\section*{Introduction}

Many currently used programming languages allow the programmer to execute some code at compile time, including C\# \cite{csharp:source_generators,roslyn}, Rust \cite{rust, klabnik2019rust} and C++ \cite{ISO:cpp20}.

>>>>

\section{Introduction}

Compile-time function execution is an aspect of a programming language, that allows the programmer to execute code at compile-time.
The goals and capabilities of CTFE depend on the language and is discussed in chapter \ref{related-work}, however it plays a secondary role in the compilation process.

CTFE first builds the compiler around the interpreter component.
The role of the compiler is to construct the semantic model
